The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-06-02 background.tex
添加新条目

\subsection{List of basic terminology} % (fold)
\label{sub:list_of_basic_terminology}
here we goes the terminology that will use in the following subsections within this section. all the related basic terms will in italics fonts.
\begin{itemize}
	\item order
	\item task
	\item resource
	\item capacity
	\item service
	\item 
\end{itemize}
% subsection list_of_basic_terminology (end)

@@

@@

\subsection{The evolution of manufacturing ecosystem} % (fold)
\label{sub:the_evolution_of_manufacturing_ecosystem}
Before the realization of the operation model mentioned above(\autoref{subs:Operation model of users}), we will analyze the evolution path in both micro and macro view of manufacturing ecosystem w.r.t. the domain in cloud manufacturing.

@@

User is the basic activity individual in the manufacturing ecosystem, the interaction between users will change their \begin{inparaenum}[1)]
\item type,
\item status and 
\item niche width
\end{inparaenum}, 
all these changes contribute to microscopic evolution of the ecosystem. More specifically, type change describes the change of user's type among pure demander, pure provider and complex user; status change describes weather a user in the ecosystem or not; niche width change describes the importance or condition of the user, especially the provider and we will only discuss the provider's niche width in this paper. \autoref{tab:userchange} concludes the appearances that we will study in this paper.

@@

\subsubsection{Macroscopic evolution} % (fold)
\label{ssub:macroscopic_evolution}

Individual evolution will lead to the evolution of the whole ecosystem and the overall effect is greater than the sum of these individuals. the amount, diversity, operation pattern recognition and service cycle rate are the topics of macroscopic evolution.

@@

\subsection{Main topics and their academic importance}
% 提一下云制造生态环境中的应用、模块，主要强调这些模块之间的交互，会产生怎样的作用。 目前云制造缺乏相关运作式的讨论，而商业模式中的不同行为会影响、改变、涌现。
As shown in \autoref{fig:structure},
Rating system, decision support system, recommender system,
detail info will seen in
Modular approaches are widely used to decompose a complex system into smaller subsystems according to their functions. For example, Yang and Li (2011) divided a cloud manufacturing services management and control platform into seven functional modules such as system management module, production management module and so on

% subsection the_evolution_of_manufacturing_ecosystem (end)
% section background (end)

>>>>

\subsection{List of basic terminology} % (fold)
\label{sub:list_of_basic_terminology}
here we goes the terminology that will use in the following subsections within this section. all the related basic terms will in italics fonts.
\begin{itemize}
	\item order
	\item task correspond to capacity
	\item resource
	\item capacity is the function of a resource. like quantity
	\item service is the bundle of capacities.
	\item 
\end{itemize}
% subsection list_of_basic_terminology (end)

@@

platform model is about the part of decision making	agent of platform.

@@

user's model is the part of decision making agent of users.

\subsection{The evolution of manufacturing ecosystem} % (fold)
\label{sub:the_evolution_of_manufacturing_ecosystem}
Before the realization of the operation model mentioned above(\autoref{subs:Operation model of users}), we will analyze the evolution path in both micro and macro view of manufacturing ecosystem w.r.t. the domain in cloud manufacturing. The overall evolution process is illustrated in \autoref{fig:overallevolution},
\begin{figure}[htbp]
	\centering
	\includegraphics[width=.5\textwidth]{evolutionview}
	\caption{Overall evolution process}
	\label{fig:overallevolution}
\end{figure}
the microscopic evolution corresponds to the change of user status while the macroscopic evolution corresponds to the change of the system status.

@@

by both type of agents, more on user agent, the platform agent will change a individual by affect the individual's decision, not directly means.

User is the basic activity individual in the manufacturing ecosystem, and their \begin{inparaenum}[1)]
\item type,
\item status and 
\item niche width
\end{inparaenum} will be changed by the decision they've made. 
All these changes contribute to microscopic evolution of the ecosystem. More specifically, type change describes the change of user's type among pure demander, pure provider and complex user; status change describes weather a user in the ecosystem or not; niche width change describes the importance or condition of the user, especially the provider and we will only discuss the provider's niche width in this paper. \autoref{tab:userchange} concludes the appearances that we will study in this paper.

@@

\subsubsection{Macroscopic evolution} % (fold)
\label{ssub:macroscopic_evolution}
Comes form both of the agents. more on platform agent.
indirect: the group effect.

Individual evolution will lead to the evolution of the whole ecosystem and the overall effect is greater than the sum of these individuals.

the amount, diversity, operation pattern recognition and service cycle rate are the topics of macroscopic evolution.

\begin{table}[htbp]
 	\caption{Macroscopic evolution}
 	\label{tab:macroevolution}
 	\centering
 	\begin{tabularx}{\textwidth}{llX}
 	\toprule
 	\textbf{column 1} & \multicolumn{2}{l}{\textbf{Appearance with concise description}} \\
 	\midrule
 	Amount & & \\
 	Diversity & & \\
 	Service cycle rate & & \\
 	\bottomrule
 	\end{tabularx}
 \end{table}

@@

\subsection{Main topics and their academic importance}
% 提一下云制造生态环境中的应用、模块，主要强调这些模块之间的交互，会产生怎样的作用。 目前云制造缺乏相关运作式的讨论，而商业模式中的不同行为会影响、改变、涌现。
As shown in \autoref{fig:structure},

the core is about the decision making all the time, individuals' decision making will affect themselves directly, that will lead to most of the microscopic evolution, and the group effective will contribute part of the macroscopic evolution

Rating system, decision support system, recommender system,
detail info will seen in
Modular approaches are widely used to decompose a complex system into smaller subsystems according to their functions. For example, Yang and Li (2011) divided a cloud manufacturing services management and control platform into seven functional modules such as system management module, production management module and so on

so, the topic here is the design of both decision making agents.
% subsection the_evolution_of_manufacturing_ecosystem (end)
% section background (end)

### 2016-06-02 head.tex
添加新条目

% 通过仿真，我们发现。。。

>>>>

% 通过仿真，我们发现。。。
In this paper, ....

Basically, (present what have done)

we do not use any utility function for the modeling; however, a unique method is proposed for eliciting the information from decision makers. The proposed model is applicable for a wide variety of multi-attribute decision making problems and can be used for  future ranking or selection without managers' judgment effort. Simulation of the managers' decisions is demonstrated in detail and the design and implementation of the model are illustrated by case study.

### 2016-06-02 method.tex
明确各agent 的划分，设计meta agent
首先要明确写作的目的，主要看看其他企业生态系统如何研究演化的。这是重点
new
添加新条目

\subsection{Modeling} % (fold)
\label{sub:modeling}

@@

Ecosystem application model including:
\subsubsection{Enterprise model}

The Model can be described with two main parts, namely object itself(attribute) and the interaction with other enterprises(function or method)

Users from platform managers, enterpirse users, customers. Even though they characteristic can be overlaped. just inherent it.

Enterprise can be described as the object with attributes like 
\begin{itemize}
	\item Rank(reputation)
	\item Resources(type, quantity, quality)
	\item Capbility
	\item Processing Status
\end{itemize}

\subsubsection{Main modules design}
\label{subsub:main_modules}

\subsubsection{System Model}
\begin{itemize}
	\item Coevolution
	\item Self-organization
	\item Emergence	
	\item Adaption
\end{itemize}

Coevolution consist of:
\begin{itemize}
	\item Scarcity of customers
	\item Conscious choice that enables the organizations to change
	\item Interconnectedness of the enables the organizations to change
	\item Feedback processes that carry the long-term consequences of coevolution
\end{itemize}

@@

% \subsection{Mathematical Formulation} % (fold)
% \label{sub:mathematical_formulation}
% \subsubsection{Comprehended Model}
% % subsection mathematical_formulation (end)

% \subsection{Verification and Validation} % (fold)
% \label{sub:verification_and_validation}

% % subsection verification_and_validation (end)

@@

\subsubsection{Logical process}
\begin{figure}[htbp]
\centering\small
\subfloat[Order Flow]{\resizebox{0.45\textwidth}{!}{\input{figures/order_flow}}\label{fig:orderflow}} \hspace{0.09\textwidth}
\subfloat[User Rank]{\resizebox{0.45\textwidth}{!}{\input{figures/user_rank}}\label{fig:userrank}}
% \resizebox{0.9\textwidth}{!}{\input{figures/simple_order_flow}}
\caption{Simple Flow Chart of Order}
% \label{fig:simpleorderflow}
\end{figure}

@@

\subsubsection{Verification and validation}
% subsection agent_based_model_and_simulation (end)
% section methodological_approach (end)

>>>>

This section starts with a brief overview of ABMS. Then .... Finally ... 
i.e. the swarm model of the system.

In a word, the center of the research is the design of the user agent, and the core of the agent is to make decisions. so the core of the evolution is to make decision?

core of the paper: agent simulation, decision making.

\subsection{Framework of Agent-based modeling} % (fold)
\label{sub:framework of agent based modeling}
\begin{figure}[htbp]
\centering\small
\subfloat[Order Flow]{\resizebox{0.45\textwidth}{!}{\input{figures/order_flow}}\label{fig:orderflow}} \hspace{0.09\textwidth}
\subfloat[User Rank]{\resizebox{0.45\textwidth}{!}{\input{figures/user_rank}}\label{fig:userrank}}
% \resizebox{0.9\textwidth}{!}{\input{figures/simple_order_flow}}
\caption{Simple Flow Chart of Order}
% \label{fig:simpleorderflow}
\end{figure}

@@

\subsection{Agents in the ecosystem model} % (fold)
\label{sub:agents_in_the_ecosystem_model}
Using UML 
% subsection agents_in_the_ecosystem_model (end)

\subsubsection{Meta agent} % (fold)
\label{ssub:meta_agent}
is a decision maker
% subsubsection meta_agent (end)

\subsubsection{User agent} % (fold)
\label{ssub:user_agent}

% subsubsection user_agent (end)

\subsubsection{Platform agent} % (fold)
\label{ssub:platform_agent}

% subsubsection platform_agent (end)

\subsection{Ecosystem model} % (fold)
\label{sub:ecosystem model}

% subsection model_realization (end)

\subsubsection{Main modules design}
\label{subsub:main_modules}
inherent relationships, execution sequence/queue.

for service provider to modify their service area, i.e. breadth and depth.

Decision making involves choosing some course of action among various alternatives. For a decision maker, fulfilling the con

\subsubsection{System Model}
\begin{itemize}
    \item Co-evolution
    \item Self-organization
    \item Emergence 
    \item Adaption
\end{itemize}

Assumptions:
\begin{enumerate}
    \item substitute transport with time consume
    \item manufacturing agent randomly show up in the map
\end{enumerate}

Co-evolution consist of:
\begin{itemize}
    \item Scarcity of customers
    \item Conscious choice that enables the organizations to change
    \item Interconnectedness of the enables the organizations to change
    \item Feedback processes that carry the long-term consequences of co-evolution
\end{itemize}

@@

\subsection{Simulation design} % (fold)
\label{sub:simulation_design}

% subsection simulation_design (end)

@@

\subsubsection{Logical process}

@@

% subsection agent_based_model_and_simulation (end)
% section methodological_approach (end)
